
\section{Experience}

% \begin{entrylist}

	\entrytable%
	{National Maritime Team Lead \& Principal Maritime and Coastal Engineer}
	{July 2023 to Present}
	{(\difftoday{2023}{07}{17})}
	{Kellogg, Brown \& Root}
	{Brisbane, Queensland}
	{\begin{itemize}
		\item Led diverse national Maritime team of ten engineers, ensuring team cohesion through effective supervision and training.
		\item Undertook roles such as Maritime Lead, Proposal Leader, and Project Manager, enhancing efficiency and project success.
		\item Aligned staff resources with forecasted sales and secured projects, improving project timelines and resource utilization.
		\item Delivered client-focused solutions, especially in Defence, establishing strong client relationships for repeat business.
		\item Executed design, and documentation for maritime projects, ensuring high-quality deliverables exceeding client expectations.
		\item Prepared compelling bids, showcasing technical capabilities, resulting in an increased project success rate.
		\item Managed projects to within timelines and budget constraints, consistently achieving milestones and client expectations.
		\item Maintained effective communication with clients, enhancing stakeholder relationships and project success.
		\item Coordinated job teams on maritime projects, providing mentorship, fostering development, and ensuring overall project success.
		\end{itemize}
	}

	\entrytable%
	{Principal Engineer Coastal Infrastructure}
	{July 2022 to July 2023}
	{(\diffdates{2022}{07}{17}{2023}{07}{17})}
	{Moreton Bay Regional Council}
	{Strathpine, Queensland}
	{\begin{itemize}
			% \item Provide specialist technical engineering advice to key stakeholders in the planning and design of coastal infrastructure and coastal management activities.
			% \item Investigate complex coastal management problems and prepare and present technical reports and recommendations.
			% \item Coordinate and/or undertake design studies to support infrastructure projects and long term strategic planning and growth (including management of specialist consultants).
			% \item Plan and deliver of coastal infrastructure and coastal management projects, including completing concept designs, preparation of cost estimates, and the acquisition of approvals.
			% \item Support the development and implementation of asset management plans, including ongoing long-term maintenance and renewal programs.
			% \item Support the development of team capability to drive a high performance, continuous improvement and customer focused culture.
			\item Delivered integrated solutions for coastal planning and design, enhancing stakeholder understanding and ensuring sustainability.
			\item Prepared technical reports to investigate coastal management problems, ensuring informed decisions and achieving project goals.
			\item Managed consultants and supported long-term planning, streamlining processes for efficient infrastructure projects.
			\item Contributed to planning and delivery of coastal projects, developing concept designs and cost estimates for successful outcomes.
			\item Supported asset management plans for coastal protection, monitoring, and planning long-term maintenance for enhanced longevity.
			\item Drove team capability for a customer-focused culture, fostering continuous improvement, and increased customer satisfaction.
			\item Built strong relationships with stakeholders, collaborating internally and externally to achieve service delivery goals.
		\end{itemize}
	}

	\entrytable%
	{Research Associate}
	{Nov 2021 to Oct 2023}
	{(2 years)}
	{The University of New South Wales -- Water Research Laboratory}
	{Sydney, New South Wales}
	{\vspace{-3\parskip}
	% \begin{itemize}
	% 		\item Developed forecasting system for coastal storm hazards, available \href{https://coastalews.wrl.unsw.edu.au/}{online}.
	% 		\item Responsible for developing methodology, models, automated workflows, and dashboard.
	% 		\item Incorporate feedback from local, state and federal government project partners.
	% 		\item Overseeing evaluation of system for to determine forecasting performance.
	% 	\end{itemize}
	}

	\entrytable%
	{Senior Coastal Engineer}
	{Feb 2021 to Sept 2022}
	{(\diffdates{2021}{02}{16}{2022}{09}{14})}
	{BMT}
	{Brisbane, Queensland}
	{
	\vspace{-3\parskip}
	% \begin{itemize}
	% 		\item Coastal and hydraulic modelling: Wave modelling, statistical downscaling, EVA
	% 		\item Maritime structural engineering: Coastal protection (armour rock, beach nourishment)
	% 		\item Business development: Proposal writing and feasibility studies
	% 	\end{itemize}
	}

	\entrytable%
	{Structural Engineer (Maritime \& Coastal)}
	{Jan 2016 to Dec 2017}
	{(2 years)}
	{Kellogg, Brown \& Root}
	{Brisbane, Queensland}
	{\vspace{-3\parskip}}

	\entrytable%
	{Graduate Structural Engineer (Maritime \& Coastal)}
	{Jan 2011 to Jan 2016}
	{(\diffdates{2011}{01}{31}{2016}{01}{31})}
	{Kellogg, Brown \& Root}
	{Brisbane, Queensland}
	{\vspace{-3\parskip}}
