\section{Projects}

	% \entrytableproject%
	% {SEA1180-1 NCIS-5 HMAS Coonawarra}
	% {2022 to Present}
	% {}
	% {Maritime Design Lead for KBR (Client: Australian Department of Defence)}
	% {Cairns, Northern Territory}
	% {Upgrade of existing wharf (including frontal pontoons) for homeporting of new Arafura Class Offshore Patrol Vessels.}
	% {Technical oversight of maritime related construction support queries, and site inspections.}

	\entrytableproject%
	{Mackay Breakwater Maintenance Strategy Assessment}
	{2023 to Present}
	{}
	{Project Manager for KBR (Client: North Queensland Bulk Ports)}
	{Mackay, Queensland}
	{Assess NQBP's existing and alternative strategies to determine if there are more efficient maintanence approaches.}
	{Project budget, client communication, technical review and oversight of modelling reporting and deliverables.}

	\entrytableproject%
	{SEA3036-1PH4 Port Hera Infrastructure Project}
	{2023 to Present}
	{}
	{Maritime Design Lead for KBR (Client: Australian Department of Defence))}
	{Hera, Timor-Leste}
	{Concept and detailed design of wharf (\SI{100}{\m} long) and access bridge {\SI{140}{\m} long in seismic area.}}
	{Engineering design oversight of drawings and reports.}

	\entrytableproject%
	{Queens Beach South Coastal Protection Upgrade}
	{2022 to 2023}
	{}
	{Principal Coastal Engineer while at Moreton Bay Regional Council}
	{Brisbane, Queensland}
	{Upgrade of beach compartment with rock revetment (\SI{230}{\m} long), rock groynes and beach nourishment (\SI{13000}{\m\cubed}).}
	{Detailed design procurement, technical review and oversight of detailed design deliverables and specifications.}
	
	\entrytableproject%
	{TE Bonney Reserve \& Oyster Point Esp. Coastal Protection Upgrade}
	{2022 to 2023}
	{}
	{Principal Coastal Engineer at Moreton Bay Regional Council}
	{Beachmere \& Scarborough, Queensland}
	{Replacement of aging and informal seawalls at two locations (total length of \SI{435}{\m}) with new rock revetement.}
	{Detailed design procurement, technical review and oversight of detailed design deliverables and specifications.}

	\entrytableproject%
	{Woody Point Crockatt Park Seawall Renewal}
	{2022 to 2023}
	{}
	{Principal Coastal Engineer at Moreton Bay Regional Council}
	{Redcliffe, Queensland}
	{Replacement of an aging reinforced concrete vertical seawall (\SI{450}{\m} long) with new pre-cast concrete stepped seawall on a popular foreshore.}
	{Technical review and oversight of detailed design and specifications.}

	\entrytableproject%
	{Deception Bay Seawalls Condition Inspection \& Options Assessment}
	{2022 to 2023}
	{}
	{Principal Coastal Engineer at Moreton Bay Regional Council}
	{Deception Bay, Queensland}
	{Review of existing conditions of \SI{2}{\km} of ageing seawall and planning of repair and renewal works.}
	{Technical review and oversight of inspection works, including geotechnical investigation and statutory approvals, and options assessment.}

	\entrytableproject%
	{Charlish Park Seawall Renewal}
	{2022 to 2023}
	{}
	{Principal Coastal Engineer at Moreton Bay Regional Council}
	{Redcliffe, Queensland}
	{Proposed demolition of an ageing reinforced concrete stepped seawall and replacement with a rock armour revetment and crest wall.}
	{Technical review and oversight of detailed design and specifications.}

	\entrytableproject%
	{Flinders Parade Cliff Protection}
	{2021 to 2023}
	{}
	{Principal Coastal Engineer at Moreton Bay Regional Council}
	{Scarborough, Queensland}
	{Proposed stabilisation of approximately \SI{150}{\m} of coastal cliffs using groyne extension works and beach nourishment.}
	{Completing detailed design and documentation, including design of groyne and nourishment works.}

	\entrytableproject%
	{Kingsford Smith Drive Upgrade}
	{2016 to 2018}
	{}
	{Structural Engineer for KBR (Client: Lendlease and Brisbane City Council)}
	{Brisbane, Queensland}
	{Road widening along the Brisbane River, including a \SI{1.2}{\km} long marine retaining wall structure with cantilevered pedestrian and cycle path.}
	{Performing detailed design calculations, writing design reports and specifications for the marine structure and associated works.}

	\entrytableproject%
	{Dawson River Flood Study}
	{2015 to 2016}
	{}
	{Civil Engineer for KBR (Client: Banana Shire Council)}
	{Banana, Queensland}
	{Stage Two flood study to understand flooding impacts and mitigate future flood risks fors located on the Dawson River, Dee River and tributaries.}
	{Developed TUFLOW models and simulated future flood scenarios to identify areas of risk.}

	\entrytableproject%
	{Callide Dam Operation Study}
	{2015 to 2016}
	{}
	{Civil Engineer for KBR (Client: QLD Department of Energy and Water Supply, \& SunWater)}
	{Biloela, Queensland}
	{Investigated the feasibility of operating Callide Dam as a flood mitigation dam after the Feb 2015 flood event.}
	{Developing dam operational models to compared operating the dam using different procedures.}

	\entrytableproject%
	{Osborne No. 1 Berth Upgrade}
	{2015}
	{}
	{Maritime Structural Engineer for KBR (Client: Flinders Port Holdings)}
	{Adelaide, South Australia}
	{Wharf strengthening concept design to enable berth to accommodate larger vessels.}
	{Performing structural engineering concept development including design drawings and options report.}

	\entrytableproject%
	{Port of Brisbane Operations \& Maintenance Studies}
	{2014 to 2018}
	{}
	{Maritime Structural Engineer for KBR (Client: Port of Brisbane)}
	{Brisbane, Queensland}
	{Conditions assessment of various existing wharf structural components to evaluate residual life and propose maintenance strategies.}
	{Performing condition inspections (visual inspections in addition to non-destructive testing), performing structural capacity calculations and writing design report.}

	\entrytableproject%
	{Burrum Heads Boat Ramp and Car Trailer Park}
	{2014 to 2015}
	{}
	{Maritime Structural Engineer for KBR (Client: QLD Department of Transport and Main Roads)}
	{Burrum Heads, Queensland}
	{New recreational boating facility, including three-lane boat ramp, floating walkway, groyne, shore protection and drainage works.}
	{Performing detailed design drawings and documentation.}

	\entrytableproject%
	{Patterson River and Queenscliff Dredging Review}
	{2014 to 2015}
	{}
	{Coastal Engineer for KBR (Client: Parks Victoria)}
	{Melbourne, Victoria}
	{Optimization of Parks Victoria's dredging program at river entrances to maintain safe boating access.}
	{Completed numerical wave and sediment transport modelling for Port Philip bay.}

	\entrytableproject%
	{Legacy Way Residential Property Condition Surveys}
	{2014}
	{}
	{Structural Engineer for KBR (Client: Transcity Joint Venture)}
	{Indooroopilly, Queensland}
	{Two bored tunnels, \SI{4.6}{\km} long, carrying two motorway grade lanes of traffic in each direction between Toowong and Kelvin Grove.}
	{Engaging with local residents and conducting dilapidation surveys to assess potential impacts of underground construction works.}

	\entrytableproject%
	{Jazan Refinery Sea Water Cooling System}
	{2012 to 2014}
	{}
	{Civil Engineer for KBR (Client: Saudi Aramco)}
	{Jazan Economic City, Saudi Arabia}
	{Green-field oil refinery with a design capacity of \num{400000} barrels per day, using a seawater cooling system with a design flow of \SI{450000}{\m\cubed\per\hour}.}
	{Hydraulic modelling to confirm performance of open-channel structures, including development of operational procedures.}

	\entrytableproject%
	{Townsville Port Inner Harbour Expansion (TPIX)}
	{2012 to 2013}
	{}
	{Maritime Structures Engineer for KBR (Client: Port of Townsville)}
	{Townsville, Queensland}
	{Reconstruction and extension of Berth 10 to accommodate military, cruise and commercial shipping, the construction of a new multi-purpose passenger terminal, and upgrade of Berth 8 to accommodate Panamax sized ships.}
	{Completing structural calculations for Berth 8 and Berth 10 works, developing design drawing and documentation, and performing site supervision of construction works.}

	\entrytableproject%
	{Gorgon LNG Construction Support}
	{2011 to 2014}
	{}
	{Maritime Structures Engineer for KBR (Client: Kellogg Joint Venture Gorgon)}
	{Barrow Island, Western Australia}
	{Australia's largest single resource project, delivering 15.6 million tonnes per annum of LNG to Western Australia.}
	{Supporting construction works, in particular a large, steel, mechanical barge ramp used. Completing structural calculations, developing design drawings and documentation.}

	\entrytableproject%
	{Margate Seawall}
	{2011 to 2014}
	{}
	{Maritime Structures Engineer for KBR (Client: Moreton Bay Regional Council)}
	{Redcliffe, Queensland}
	{Detailed design of a 150 m segment of cast insitu, reinforced concrete, stepped seawall that uses vinyl sheet piling to limit the effects of scour.}
	{Completing detailed design and documentation of precast stepped seawall.}


% \begin{entrylist}
% 	\entry%
% 	{2014--15}
% 	{Wave Buoy Data Recovery, Processing and Management}
% 	{Deagon, Queensland}
% 	{\whileatfor{KBR}{Coastal Impacts Unit (Queensland Government)} \\
% 		Produced and documented MATLAB and Python scripts to consolidate historical wave buoy data.}
% \end{entrylist}



% \begin{entrylist}
% \entry%
% {2011--12}
% {Browse LNG Port Operability Study}
% {James Price Point, Western Australia}
% {\emph{Woodside Energy} \\
% Identified critical sea states for using wave hindcast data for use in mooring analysis.}
% \end{entrylist}

