
\section{volunteer}


\begin{entrylist}
\entry%
{2019--20}
{UNSW WRL Research Management Group (RMG)}
{Sydney, New South Wales}
{\emph{PhD student representative} \\
The RMG identifies opportunities and addresses issues regarding WRL's research output.
\begin{itemize}
\item Managing creation of WRL webpage to showcase current PhD students and provide information to prospective students.
\item Organising social events between research and project staff to encourage collaboration.
\end{itemize}}
\end{entrylist}



\begin{entrylist}
\entry%
{2012--15}
{Young Engineers Australia Queensland}
{Brisbane, Queensland}
{\emph{Treasurer} \\
YEAQ is a special interest group of Engineers Australia aimed at supporting young engineers.
\begin{itemize}
\item Budgeted, managed and monitored the group's finances
\item Attracted over \$25,000 in industry sponsorship during the '13--'14 financial year.
\item Advised the committee on strategy to ensure events and initiatives were financially feasible.
\item Responsible for financial administration; keeping up-to-date records and ensuring the group complied with internal processes and procedures.
\end{itemize}}
\end{entrylist}

\begin{entrylist}
\entry%
{2012--15}
{IMPACT (KBR Graduate Program)}
{Brisbane, Australia}
{\emph{Graduate Program Coordinator} \\
IMPACT is a network of developing professionals with 0--7 years of experience within KBR.
\begin{itemize}
\item Involved on a state and national level to deliver training and social activities to graduates.
\item Proposed and monitored budget for social activities.
\item Coordinated Australia's participation in company-wide events, such as Green Week and Global Week.
\end{itemize}}
\end{entrylist}

