%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[print]{friggeri}
\usepackage{multicol}
\usepackage{changepage}
\usepackage{ifthen}
\usepackage{changepage}

% Match double quotes
% https://tex.stackexchange.com/a/52354
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

\newcommand{\forweb}{false} % censor items if outputting web

\setlength{\columnsep}{0cm}

\begin{document}

\header{chris}{leaman}{chartered professional maritime \& coastal engineer}
\vspace{0.1cm} % ADJUST THIS TO PUSH CONTENTS UP/DOWN THE PAGE


%-----------------------
%   SUMMARY SECTION
%-----------------------

\section{professional summary}
\begin{adjustwidth}{2cm}{}
  Current PhD Student at UNSW WRL, investigating regional scale storm wave forecasting in the context of an Australian coastal hazards Early Warning System.
  Chartered Professional coastal and maritime engineer (CPEng \& RPEQ) with a variety of extensive skills in structural engineering, coastal modelling, and hydraulic modelling.
  Seven years of diverse experience as an engineering consultant, demonstrating adaptability and flexibility to work effectively in autonomous and team environments.\\
  \vspace{-2\parskip}
\end{adjustwidth}

%---------------------------
%	CONTACT SECTION
%---------------------------

% \ifdefined\isweb%
%   \input{contact-web.tex}
%   \else
%   \input{contact-personal.tex}
% \fi

\input{contact-web.tex}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}
\begin{entrylist}
  %------------------------------------------------
\entry%
{2018--22}
{Doctor of Philosophy {\normalfont (Coastal Engineering)}}%
{Sydney, New South Wales}
{\emph{The University of New South Wales - Water Research Laboratory}
  \begin{itemize}
  \item Research topic: \textit{`Novel Remote Sensing and Machine Learning Applications for Regional Storm Wave Runup Forecasting`}
  \end{itemize}
}

%------------------------------------------------
\entry%
{2007--10}
{Bachelor of Engineering {\normalfont (Extended Major in Civil Engineering) (Hons. IIA)}}%
{Brisbane, Queensland}
{\emph{The University of Queensland}
}
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{positions held}

\begin{entrylist}

\entry%
{2017--18\\
2011--16}
{\vspace*{-4.6ex}\\Structural Engineer (Maritime \& Coastal)\\
Graduate Structural Engineer (Maritime \& Coastal)}%
{Brisbane, Queensland}
{\emph{Kellogg, Brown \& Root}}

& Key skills and responsibilities:\\

\entrybulletsindented%
{}
{Coastal, hydraulic and hydrologic modelling}
{}
{\begin{itemize}
\item Modelling coastal processes including waves and sediment transport using DELFT3D
\item Building and developing TUFLOW models to simulate flood events
\item Developing flood studies and risk assessments for regional towns and rail tracks
\end{itemize}
}

\entrybulletsindented%
{}
{Structural engineering of maritime structures}
{}
{\begin{itemize}
  \item Completing structural design and detailing of wharves, dolphins, sea walls and ramps
  \item Performing complex finite element analysis using Strand7
  \item Inspecting site works for design verification and construction support purposes
\end{itemize}
}

\entrybulletsindented%
{}
{Programming and documentation}
{}
{\begin{itemize}
\item Developing Excel VBA and Python scripts to perform large scale, complex analysis
\item Writing technical reports, specification and proposal documents

\end{itemize}}



%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	SOFTWARE SECTION
%----------------------------------------------------------------------------------------

% \section{software}
% \begin{adjustwidth}{2cm}{}
% \vspace{-2\parskip}
% \begin{multicols}{4}
% DELFT3D\\
% MIKE21\\
% TUFLOW\\
% \\
% Python\\
% Excel VBA\\
% MATLAB\\
% \\
% AutoCAD\\
% \LaTeX\\
% ArcGIS\\
% \\
% Strand7\\
% Microstran\\
% STAAD Pro\\
% \end{multicols}
% \vspace{-3\parskip}
% \end{adjustwidth}


%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------
\section{professional memberships}
\begin{entrylist}
%------------------------------------------------
\entry%
{since 2017}
{Chartered Professional Engineer {\normalfont (CPEng) (Structural)}\\
National Engineering Register {\normalfont (NER) (Structural)}}%
{}
{\emph{Engineers Australia}
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}
\begin{adjustwidth}{2cm}{}
Stewart, J \& Leaman, C 2013 'Validation of dredge plume modeling inputs', in {\emph{Coasts \& Ports 2013 Conference: 21st Australasian Coastal and Ocean Engineering Conference, Sydney N.S.W.}} Ed. Turner, I \& Couriel E. Barton, A.C.T: Engineers Australia, 2013
\end{adjustwidth}




%----------------------------------------------------------------------------------------


%-----------------------------------------------------------------------------------------
%	PROJECTS SECTION
% ----------------------------------------------------------------------------------------
\newpage

\section{hydraulic/coastal modelling projects}

\begin{entrylist}
\entry%
{since 2015}
{Callide Dam Operation Study}
{Biloela, Queensland}
{\emph{Department of Energy and Water Supply (Queensland Government) and SunWater} \\
Investigated the feasibility of operating Callide Dam as a flood mitigation dam after the Feb 2015 flood event. Used Python to conduct numerical dam simulation and automate plotting of results. }
\end{entrylist}

\begin{entrylist}
\entry%
{2015--2016}
{Dawson River Flood Study}
{Banana, Queensland}
{\emph{Banana Shire Council} \\
Developed TUFLOW models and simulated future flood scenarios to identify areas of risk. }
\end{entrylist}

\begin{entrylist}
\entry%
{2015}
{ARTC Track Drainage Risk Assessment}
{Tarcoola, South Australia}
{\emph{Australian Rail Track Corporation} \\
Assessed risk of rail track overtopping during flood events using catchment analysis.}
\end{entrylist}

\begin{entrylist}
\entry%
{2014--15}
{Patterson River and Queenscliff Dredging Review}
{Melbourne, Victoria}
{\emph{Parks Victoria} \\
Completed modelling of Port Philip bay to optimize Parks Victoria's dredging program at river entrances.}
\end{entrylist}

\begin{entrylist}
\entry%
{2014--15}
{Wave Buoy Data Recovery, Processing and Management}
{Deagon, Queensland}
{\emph{Coastal Impacts Unit (Queensland Government)} \\
Produced and documented MATLAB and Python scripts to consolidate historical wave buoy data.}
\end{entrylist}

% \begin{entrylist}
% \entry%
% {2012--14}
% {Jazan Refinery Sea Water Cooling System}
% {Jazan Economic City, Saudi Arabia}
% {\emph{Saudi Aramco} \\
% Evaluated hydraulic performance of cooling system under varying operational conditions.}
% \end{entrylist}


\begin{entrylist}
\entry%
{2011--12}
{Browse LNG Port Operability Study}
{James Price Point, Western Australia}
{\emph{Woodside Energy} \\
Identified critical sea states for using wave hindcast data for use in mooring analysis.}
\end{entrylist}
\\


\section{ structural engineering projects}

\begin{entrylist}
\entry%
{since 2016}
{Kingsford Smith Drive Upgrade}
{Brisbane, Queensland}
{\emph{Lendlease/Brisbane City Council} \\
Performed detailed design of cantilever retaining wall structure for road widening over the Brisbane River. Used Python to complete optimised structural design of piled retaining wall structure in highly variable geotechnical conditions.
}
\end{entrylist}

\begin{entrylist}
\entry%
{2015}
{Osborne No. 1 Berth Upgrade}
{Adelaide, Queensland}
{\emph{Flinders Port Holdings Pty Ltd} \\
Developed wharf strengthening concept design to enable berth to accommodate larger vessels.}
\end{entrylist}

\begin{entrylist}
\entry%
{since 2014}
{Port of Brisbane Operations \& Maintenance Studies}
{Brisbane, Queensland}
{\emph{Port of Brisbane Pty Ltd} \\
Conducted assessment of various existing wharf structural components at the Port of Brisbane.}
\end{entrylist}

\begin{entrylist}
\entry%
{2014--15}
{Burrum Heads Boat Ramp and Car Trailer Park}
{Burrum Heads, Queensland}
{\emph{Department of Transport and Main Roads (Queensland Government)} \\
Completed detail design new boat ramp facilities, groyne, shore protection and drainage works.}
\end{entrylist}

\begin{entrylist}
\entry%
{2014}
{Legacy Way Residential Property Condition Surveys}
{Indooroopilly, Queensland}
{\emph{Transcity Joint Venture} \\
Conducted condition surveys of nearby residential buildings to assess impacts of construction works.}
\end{entrylist}


\begin{entrylist}
\entry%
{2012--13}
{Townsville Port Inner Harbour Expansion (TPIX)}
{Townsville, Queensland}
{\emph{Port of Townsville} \\
Completed detailed design and site supervision of berth upgrade and new cruise terminal building works.}
\end{entrylist}

% \begin{entrylist}
% \entry%
% {2012}
% {East Swanson Dock Crane Unloading Verification}
% {Melbourne, Victoria}
% {\emph{Patrick Terminals} \\
% Assessed capacity of wharf under temporary loads imposed by new quay container crane unloading.}
% \end{entrylist}

\begin{entrylist}
\entry%
{2011--14}
{Gorgon LNG Construction Support}
{Barrow Island, Western Australia}
{\emph{Chevron Australia} \\
Performed detailed design and provided site support for a large steel mechanical barge ramp.}
\end{entrylist}

% \begin{entrylist}
% \entry%
% {2011--12}
% {Margate Seawall}
% {Redcliffe, Queensland}
% {\emph{Moreton Bay Regional Council} \\
% Completed detailed design of precast stepped sea wall units to combat erosion of shoreline. }
% \end{entrylist}


%----------------------------------------------------------------------------------------
%	VOLUNTEER SECTION
%----------------------------------------------------------------------------------------
\newpage

\section{volunteer}

\begin{entrylist}
\entry%
{2012--15}
{Young Engineers Australia Queensland}
{Brisbane, Queensland}
{\emph{Treasurer} \\
YEAQ is a special interest group of Engineers Australia aimed at supporting young engineers.
\begin{itemize}
\item Budgeted, managed and monitored the group's finances
\item Attracted over \$25,000 in industry sponsorship during the '13--'14 financial year.
\item Advised the committee on strategy to ensure events and initiatives were financially feasible.
\item Responsible for financial administration; keeping up-to-date records and ensuring the group complied with internal processes and procedures.
\end{itemize}}
\end{entrylist}

\begin{entrylist}
\entry%
{2012--15}
{IMPACT (KBR Graduate Program)}
{Brisbane, Australia}
{\emph{Graduate Program Coordinator} \\
IMPACT is a network of developing professionals with 0--7 years of experience within KBR.
\begin{itemize}
\item Involved on a state and national level to deliver training and social activities to graduates.
\item Proposed and monitored budget for social activities.
\item Coordinated Australia's participation in company-wide events, such as Green Week and Global Week.
\end{itemize}}
\end{entrylist}


\end{document}
%%% Local Variables:
%%% mode: LaTeX
%%% TeX-PDF-mode: t
%%% TeX-engine: xetex
%%% End:
